% Synthetic test file for the ECEB style linter (scripts/lint_euclid_style.py).
%
% Each violation line is marked with:    % EXPECT: <rule_id>
% Each clean counterpart is marked with: % CLEAN: <rule_id>
% Document-level expectations use:       % EXPECT_DOC: <rule_id>
% Edge cases use:                        % EDGE: <label>
%
% The linter should flag every EXPECT line and skip every CLEAN line.

% ====================================================================
% PREAMBLE — must be entirely skipped by the linter
% ====================================================================
\documentclass{article}
\usepackage{amsmath}
\usepackage{hyperref}
\newcommand{\Euclid}{\textit{Euclid}}
\newcommand{\IE}{$I_{\mathrm{E}}$}
\newcommand{\YE}{$Y_{\mathrm{E}}$}
\newcommand{\JE}{$J_{\mathrm{E}}$}
\newcommand{\HE}{$H_{\mathrm{E}}$}
% Preamble must NOT trigger rules even with violations present:
% dataset color analyze gray percent favor catalog comprised of
\definecolor{gray}{HTML}{808080}
\definecolor{lightgray}{gray}{0.9}

\begin{document}

% ====================================================================
% NAMING & TERMINOLOGY (N01--N10)
% ====================================================================

The Euclid mission observed the deep fields. % EXPECT: N01
The \Euclid\ mission observed the deep fields. % CLEAN: N01

The \textit{Euclid} Consortium approved the results. % EXPECT: N02
The Euclid Consortium approved the results. % CLEAN: N02

The \textsc{VIS} instrument was calibrated. % EXPECT: N03
The VIS instrument was calibrated. % CLEAN: N03

Observations were taken in the IE band. % EXPECT: N04
Observations were taken in the \IE\ band. % CLEAN: N04

We used the full dataset for training. % EXPECT: N05
We used the full data set for training. % CLEAN: N05

The sample is comprised of 500 galaxies. % EXPECT: N06
The sample is composed of 500 galaxies. % CLEAN: N06

The catalogue is publically available. % EXPECT: N07
The catalogue is publicly available. % CLEAN: N07

We achieved a high S/N ratio in all bands. % EXPECT: N08
We achieved a high S/N in all bands. % CLEAN: N08

The modelisation of the PSF is critical. % EXPECT: N09
The modelling of the PSF is critical. % CLEAN: N09

The errors associated to this method are small. % EXPECT: N10
The errors associated with this method are small. % CLEAN: N10

% ====================================================================
% BRITISH ENGLISH (E01--E08)
% ====================================================================

We analyze the photometric redshifts. % EXPECT: E01
We analyse the photometric redshifts. % CLEAN: E01

This accounts for 30 percent of the sample. % EXPECT: E02
This accounts for 30 per cent of the sample. % CLEAN: E02

The background appears gray in the image. % EXPECT: E03
The background appears grey in the image. % CLEAN: E03

See the acknowledgment section below. % EXPECT: E04
See the acknowledgement section below. % CLEAN: E04

Accurate modeling requires good data. % EXPECT: E05
Accurate modelling requires good data. % CLEAN: E05

Each source is labeled with a unique ID. % EXPECT: E06
Each source is labelled with a unique ID. % CLEAN: E06

We cross-matched the catalog with SDSS. % EXPECT: E07
We cross-matched the catalogue with SDSS. % CLEAN: E07

Results favor a flat universe. % EXPECT: E08
Results favour a flat universe. % CLEAN: E08

% ====================================================================
% UNITS & NUMBERS (U01, U02, U03, U05, U07)
% ====================================================================

The velocity dispersion is 300 km/s in the core. % EXPECT: U01
The velocity dispersion is 300\,km\,s$^{-1}$ in the core. % CLEAN: U01

Separations were measured in arcsecs from the centre. % EXPECT: U02
Separations were measured in arcsec from the centre. % CLEAN: U02

The resolution is 5arcsec in all bands. % EXPECT: U03
The resolution is 5\,arcsec in all bands. % CLEAN: U03

The luminosity is 3e5 solar luminosities. % EXPECT: U05
The luminosity is $3 \times 10^{5}$ solar luminosities. % CLEAN: U05

The catalogue contains 10,000 sources. % EXPECT: U07
The catalogue contains 10\,000 sources. % CLEAN: U07

% ====================================================================
% TYPESETTING (T01, T02, T04, T05, T06, T08)
% ====================================================================

The so-called "standard" candles were observed. % EXPECT: T01
The so-called ``standard'' candles were observed. % CLEAN: T01

We found (20-25) candidate sources per field. % EXPECT: T02
We found (20--25) candidate sources per field. % CLEAN: T02

The fit gives $log(L) = 42.3$ for the sample. % EXPECT: T04
The fit gives $\log(L) = 42.3$ for the sample. % CLEAN: T04

This paragraph ends with a forced line break.\\ % EXPECT: T05
This paragraph ends normally. % CLEAN: T05

See the documentation at https://euclid.esa.int for details. % EXPECT: T06
See the documentation at \url{https://euclid.esa.int} for details. % CLEAN: T06

Fig. 1 shows the photometric residuals. % EXPECT: T08
Figure 1 shows the photometric residuals. % CLEAN: T08

% ====================================================================
% REFERENCES & CITATIONS (R02, R03, R04)
% ====================================================================

Euclid Collaboration et al. (2024) reported the calibration. % EXPECT: R02
Euclid Collaboration: Scaramella et al. (2024) reported the calibration. % CLEAN: R02

% This old paragraph was part of an earlier draft and should have been deleted before the final submission % EXPECT: R03
% Short note % CLEAN: R03

% R04 is a document-level check: absence of the AckEC macro means it fires % EXPECT_DOC: R04

% ====================================================================
% STYLE GUIDE SPECIFIC (S01--S04)
% ====================================================================

The DEC of the target is measured precisely. % EXPECT: S01
The Dec of the target is measured precisely. % CLEAN: S01

The distribution is nonGaussian in the tails. % EXPECT: S02
The distribution is non-Gaussian in the tails. % CLEAN: S02

Deep imaging in the J band reached 26 mag. % EXPECT: S03
Deep imaging in the $\textit{J}$ band reached 26 mag. % CLEAN: S03

The data is consistent with earlier measurements. % EXPECT: S04
The data are consistent with earlier measurements. % CLEAN: S04

% ====================================================================
% EDGE CASES — must NOT produce false positives
% ====================================================================

% Edge: \definecolor{gray} in body must NOT trigger E03/E01
\definecolor{mygray}{gray}{0.5} % EDGE: E03-definecolor

% Edge: \newcommand with Euclid must NOT trigger N01
\newcommand{\MyEuclid}{\textit{Euclid}} % EDGE: N01-newcommand

% Edge: \url{} wrapping must NOT trigger T06
Visit \url{http://example.com/data} for details. % EDGE: T06-url

% Edge: math content must NOT trigger U01
The velocity is $v = 300\,\mathrm{km\,s^{-1}}$ in the cluster. % EDGE: U01-math

% Edge: \texttt{} must NOT trigger E01
Use the \texttt{color} keyword in the configuration file. % EDGE: E01-texttt

% Edge: verbatim environment must NOT trigger N05
\begin{verbatim}
dataset = load("input.csv")
color = "gray"
\end{verbatim}

% Edge: display math (equation env) must NOT trigger T04
\begin{equation}
\log_{10} x = y
\end{equation}

% Edge: nested environments (aligned inside equation inside figure)
\begin{figure}
\begin{equation}
\begin{aligned}
  a &= b + c \\
  d &= e \times f
\end{aligned}
\end{equation}
\caption{Test figure.}
\end{figure}

% Edge: \ac{} macros must NOT trigger N01
The \ac{Euclid} mission is described in detail. % EDGE: N01-ac

% Edge: \href{url}{text} must NOT trigger T06
See \href{https://euclid.esa.int}{the website} for more. % EDGE: T06-href

% Edge: inline math with \, before unit must NOT trigger U03
The distance is $5\,\mathrm{arcsec}$ from the centre. % EDGE: U03-math

% Edge: number range inside \ref must NOT trigger T02
See Table~\ref{tab2-5} for a summary. % EDGE: T02-ref

% Edge: \textit{Euclid} (correct usage) must NOT trigger N01
The \textit{Euclid} satellite was launched in 2023. % EDGE: N01-textit

% Edge: R.A. test for S01
The R.A. of the cluster is measured. % EXPECT: S01

% Edge: ORCID line must NOT trigger T02
\and J.~Smith\orcid{0000-0002-5258-8761}\inst{\ref{aff3}} % EDGE: T02-orcid

% Edge: affiliation address must NOT trigger T02
Kavli Institute, Chiba 277-8583, Japan\label{aff103} % EDGE: T02-address

% Edge: {\tt Euclid Emulator} must NOT trigger N01
The {\tt Euclid Emulator 2} reproduces nonlinear clustering. % EDGE: N01-tt

% Edge: "Center for" (institution name) must NOT trigger E01
Center for Computational Astrophysics, New York. % EDGE: E01-institution

% Edge: \begin{center} must NOT trigger E01
\begin{center}
This text is centred.
\end{center}

% Edge: postal code must NOT trigger U05
NRC Herzberg, Victoria, BC V9E 2E7, Canada\label{aff224} % EDGE: U05-postal

\end{document}
